\documentclass[12pt]{article}
\rmfamily
\usepackage[margin=1.0in]{geometry}

\title{Security of Real Systems Pentest Report}
\date{December 2020}
\author{Will Goodman}

\begin{document}
  \maketitle

  \section{Assess the System}
  In this section I analysed the system and make some recommendations to improve the existing security techniques being used.

  The server was identified as a Debian (10 or greater) server with the following open ports:
  \begin{itemize}
    \item 22 - SSH
    \item 80 - HTTP (nginx)
    \item 443 - HTTPS (nginx)
  \end{itemize}
  In addition, the following ports are filtered:
  \begin{itemize}
    \item 135
    \item 139
  \end{itemize}

  \subsection{Port 22 - SSH}
  Ideally this port should only be open if it is really required.
  If it is not completely necessary, then disable SSH.

  Only public key encryption is enabled, which reduces the security risks as brute-forcing passwords is not possible.
  However, it is imperative that the keys are kept secure on the devices where they are stored.
  If encrypted hard-drives are not already part of the security policy, they should be encrypted as soon as possible.

  There were no known CVE vulnerabilities found on this implementation of SSH.

  \subsection{Port 80 - HTTP}
  Running the nmap http-enum script reveals no pages other than index.html.
  I would recommend adding a security.txt (https://tools.ietf.org/html/draft-foudil-securitytxt-10) containing contact details in case a third-party finds a vulnerability and wishes to make the CISO aware.
  Although there is currently no robots.txt, it is important not to list any admin or secure pages if one is ever added.

  An nmap vulnerability scan of the port revealed no known CSRF or XSS vulnerabilities.

  Although HTTP has largely been surpassed by HTTPS, this port should still be left open as HSTS preloading does not appear to be in place for this system (discussed further in section 2.1).

  \subsection{Port 443 - HTTPS}
  The server only supports TLS 1.2 and 1.3.
  This is the best option at the moment as TLS 1.3 is still in development and not supported by all clients.
  The server also prefers to use the more secure TLS 1.3, which is what I would recommend.
  
  The following cipher suites are supported:
  \paragraph{TLS 1.3}
  \begin{itemize}
    \item TLS\_AES\_256\_GCM\_SHA384
    \item TLS\_CHACHA20\_POLY1305\_SHA256
    \item TLS\_AES\_128\_GCM\_SHA256
  \end{itemize}
  \paragraph{TLS 1.2}:
  \begin{itemize}
    \item TLS\_ECDHE\_RSA\_WITH\_AES\_128\_GCM\_SHA256
    \item TLS\_ECDHE\_RSA\_WITH\_AES\_128\_CBC\_SHA256
  \end{itemize}

  In general these cipher suites are deemed secure by modern standards, and achieve an $A^+$ score on SSLLabs.
  That being said, I would recommend disabling TLS\_ECDHE\_RSA\_WITH\_AES\_128\_CBC\_SHA256 or changing it to the 256-bit AES version.
  CBC AES with a 128-bit key is now considered weak by modern standards.

  The certificate appears to be a Let's Encrypt certificate with a three month validity.
  I generally would recommend a longer certificate validity period (12 months), however 3 months is the maximum length for Let's Encrypt so that cannot change.

  An nmap vulnerability scan of port 443 revealed no known CSRF or XSS vulnerabilities.

  However, the server appears to be vulnerable to a Denial-of-Service attack on an Apache server (CVE-2011-3192).
  This vulnerability is rated 7.8 (HIGH) on the Common Vulnerability Scoring System Calculator and must be fixed or mitigated as a matter of urgency.
  If the Apache server is hosted behind nginx, I would recommend ensuring that Apache only listens on localhost (127.0.0.1) to reduce the attack surface.
  In addition, make sure the version of Apache is up-to-date and potentially look at putting some improved DoS prevention measures in place.

  \subsection{Ports 135/139}
  These ports are shown as filtered due to no response being received.
  If these are not required, then ensure they are closed.
  I have not been able to find any vulnerabilities or access any services on either of these ports, so if they are required they appear to be secure.

  \subsection{Summary}
  I recommend the following changes:
  \begin{itemize}
    \item Fix Apache server so it is not vulnerable to CVE-2011-3192
    \item Enforce encrypted hard-drives as standard
    \item Either remove the 128-bit AES CBC cipher suite or upgrade it to the 256-bit version
    \item Check if ports 135/139 are open. Close them if not needed
    \item Invest in some improved DoS protection
  \end{itemize}

  \section{Explain the System}

  The server has a few specific security features configured, which I explain in more detail in this section.

  \subsection{Host-Strict-Transport-Security}
  HSTS requires browsers to use HTTPS instead of HTTP for a set period of time.
  If a browser cannot ensure the security of the connection, for example if it does not trust the provided certificate, according to the specification it should terminate the connection.
  This helps prevent Man-in-the-Middle attacks by using an encrypted connection (HTTPS) rather than plaintext which can be altered (HTTP).

  On this server, HSTS is enabled with a period of 31,536,000 seconds (one year).

  One vulnerability of HSTS is if the initial connection, or the first connection after the period expires, is over HTTP.
  To help prevent this, HSTS can be preloaded into browsers so that they know a server uses HSTS (and supports HTTPS) before sending any requests.
  However, the servers which can be preloaded must be statically set in browsers, and this server is not preloaded by any of the main browsers.
  
  HSTS still provides a security benefit in this instance, and the long timeout period reduces how often a plaintext packet may be sent.
  However, for the full benefit this browser would need to be preloaded.

  \subsection{Online Certificate Status Protocol Stapling}
  OCSP Stapling allows a server to append (staple) a time-stamped OCSP response signed by a Certificate Authority to the initial TLS handshake.
  This has two main benefits: performance and privacy.
  As the server contacts the OCSP server, only one request needs to be made as opposed to one request per client if OCSP stapling was not used.
  Since the clients never need to contact the OCSP server (the stapled certificate must be signed by the CA, so cannot be faked), the clients' browsing habits are never revealed to a third-party.
  
  On this server, OCSP Stapling is enabled, and it appears the stapled certificate is updated on a weekly basis.

  However, the OCSP ``Must-Staple'' flag is not enabled.
  I explain further in section 3.2 the benefits of enabling this flag.

  \subsection{Content Security Policy}
  A Content Security policy ("content-security-policy" header) restricts what resources within the browser, such as JavaScript or CSS, can do.
  It can help protect against Cross-Site-Scripting attacks.

  The server has the following content-security-policy header:
  \begin{verbatim}
  report-uri https://batten.report-uri.com/r/d/csp/enforce; 
  upgrade-insecure-requests; 
  default-src 'self'; 
  plugin-types application/pdf; 
  frame-ancestors 'self'; 
  img-src 'self' https:; 
  style-src 'self' https://www.batten.eu.org; 
  font-src 'self' data:
  \end{verbatim}

  This header provides improved security, although could be improved.

  The ``report-uri'' flag sends reports about violations of the policy to the given URL.
  This is very useful in a development environment when testing the CSP, however for a production website I would recommend removing it to ensure the CSP is enforced.

  The ``upgrade-insecure-requests'' flag tells the client to upgrade any HTTP link to HTTPS in case any legacy links exist.
  As this is a new website it would be best practice to make any links HTTPS anyway, however adding this flag acts as a safeguard.

  The ``plugin-types'' flag only allows the PDF plugin, and other plugins such as Flash/Java Applets will be blocked.
  This is much more secure than having no CSP, however I did not find any PDF files within the website.
  If no PDF files exist on the website, then this flag could be removed and replaced with an ``object-src `none' '' flag to block all plugins, which would be slightly more secure.

  The ``frame-ancestors'' and ``*-src'' flags tell the client where they can fetch resources from (up to two available sources).
  The `self' configuration tells the client that resources can only be collected from the same URL as the webpage, this is deemed secure.
  The `https:' flag allows images to be collected from any HTTPS URL.
  This is not as secure as a specified URL (such as in `style-src'), however is still deemed secure enough to be acceptable.
  The `font-src' flag has `data:' specified as a source, this is deemed insecure as an attacker could inject arbitrary data.
  This should be changed out for `https:' as a priority.

  \section{Extend the System}

  There are a few security features which have not been configured.
  In this section I will explain what these are, how they could improve security, and the potential risks of not enabling them.

  \subsection{Certificate Authority Authorization (CAA)}
  A CAA record specifies which Certificate Authorities can issue certificates for a given domain name.
  Without a CAA record present, any CA can issue a certificate for the domain.
  This creates a clear security flaw where the security of the domain's certificate relies on the security and integrity of many CAs.
  
  If an attacker managed to find a corrupt or insecure CA, they may be able to obtain their own valid certificate for this server's domain.
  With this certificate they could setup their own server and intercept traffic from users intending to visit your website, without the users knowing.

  I would recommend adding a CAA record specifying that only Let's Encrypt certificates are valid for this domain to reduce the likelihood of this attack.
  Currently Let's Encrypt is trusted, however it is worth keeping track of their reputation to ensure they themselves do not become corrupt.


  \subsection{Enforced OCSP Stapling}
  This was also briefly mentioned in section 2.2.
  
  On this server, the ``Must-Staple'' flag is disabled, meaning that if no OCSP signature is stapled to the certificate, the client will contact an OCSP server itself to check if the certificate is valid.
  If no response is received from the OCSP server, then the client defaults to assume the certificate is valid.
  This has a clear security flaw, as all an attacker needs to do is block the client's OCSP request.

  By enabling the ``Must-Staple'' flag, the client will close the connection if the stapled OCSP signature is missing.
  This will greatly improve security and should be enabled as soon as possible.


  \subsection{Extended Validation Certificate}
  The certificate provided for the server is a Domain Validation certificate, not Extended Validation.
  With an EV certificate, the owner of the website goes through an identity verification process.
  This identity information is then included within the certificate.
  This is a more in-depth process than for the other options (Organization Validated and Domain Validated).

  One of the benefits of upgrading to an EV certificate is that the website is much more trustworthy.
  As phishing scams have become more sophisticated, DV certificates have become more common on phishing websites.
  By upgrading to an EV certificate, any potential users would be able to check with confidence that they are on the correct website before entering any details.

  Currently, I do not believe upgrading to an EV certificate is worth doing.
  The website does not currently have any webpages where secure information must be entered, so the dangers of someone going to a phishing website are minimal.
  In addition, Let's Encrypt does not currently offer EV certificates, so you would have to spend money using a different CA.
  If the website is ever updated to require users to enter sensitive information, for example banking details, then this decision should be reconsidered.


  \subsection{Further Features}
  There are a few features which are currently disabled on the server, and should remain disabled as they are deprecated:
  \begin{itemize}
    \item HTTP Public Key Pinning
    \item SSL v2.0
    \item 0-RTT Handshakes (not deprecated, although not forward-secret and hence not as secure)
  \end{itemize}

\end{document}